Mass surveillance in cyberspace and the lost art of keeping a secret\thanks{The ideas discussed here first appeared as a DCSS project conference talk and were subsequently fleshed out in paper due to serendipitous encounters fostered by twitter.}

### 2015-07-08 edemocracy.tex
added NIFTy ack

\title{Mass surveillance in cyberspace and the lost art of keeping a secret\thanks{The ideas presented in this paper first appeared as a talk at the 2015 International Conference on Digital Citizenship and Surveillance Society in Cardiff in June 2015 and subsequently refined and developed into this paper via serendipitous encounters that were enabled by the social medium of Twitter.}}
\subtitle{Policy lessons for nation-states after the Snowden leaks}

>>>>

\title{Mass surveillance in cyberspace and the lost art of keeping a secret\thanks{The ideas presented in this paper first appeared as a talk at the 2015 Conference on Digital Citizenship and Surveillance Society in Cardiff in June 2015 and subsequently refined and developed into this paper via serendipitous encounters that were enabled by the social medium of Twitter. The work has been sponsored in part by the European Commission through project NIFTy (ISEC 2012 Action Grants HOME/2012/ISEC/INT/4000003892).}}
\subtitle{Policy lessons for nation-states after the Snowden leaks}
